A compact program for 3D passive seismic source-location imaging

### 2021-06-30 passive/paper.tex
2021年 5月13日 星期四 10时32分58秒 CDT
Wed Jun 30 14:45:32 CDT 2021

\title{A compact program for 3D passive seismic \\
source-location imaging}

\author{Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5] }
%\author{Authors}

@@

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
%yangkang.chen@zju.edu.cn \\
\footnotemark[2]
ENSN Lab \\
Seismology Department \\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt\\
engomar91@ gmail.com\\
\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[4]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
\footnotemark[5]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

@@

\section{Data and Resources}
All datasets and source codes associated with this research are hosted via the Madagascar platform (www.ahay.org) in the form of reproducible research \cite[]{mada2013}.

@@

\inputdir{mod3d_geo}
\plot{data}{width=0.6\textwidth}{Recorded passive seismic data in the synthetic example.}
\multiplot{9}{vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}{width=0.3\textwidth}{\wen{Velocity model and the highlighted first source location (a), its time-reversal imaging result using the traditional (b) and proposed (c) methods. Velocity model and the highlighted second source location (d), its time-reversal imaging result using the traditional (e) and proposed (f) methods. Velocity model and the highlighted third source location (g), its time-reversal imaging result using the traditional (h) and proposed (i) methods.}}
\multiplot{4}{data_mask0,data_mask1,data_mask2,data_mask3}{width=0.45\textwidth}{Four grouped recorded passive seismic data. }

\inputdir{field3d_geo}
%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example. (a) Recorded microseismic data. (b) Constructed velocity model. \dlo{(c) 3D source location image.}\wen{(c) 3D source location image using the traditional method. (d) 3D source location image using the proposed method.}}

\inputdir{mod3d_geo_ng}
\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }

\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }

\inputdir{mod3d_geo_noise}
\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. }

\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. }

%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
%   0:        -1.957
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
%   0:        -4.967
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
%   0:        -14.98
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
%   0:        -21.96
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
%   0:        -31.96
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
%   0:        -34.97
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
%   0:        -37.98
%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
%   0:        -41.96
%

\inputdir{mod3d_geo_density}
\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }

\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively. }

\bibliographystyle{seg}
\bibliography{micro}

%\clearpage
%Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
%\footnotemark[1]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%chenyk2016@gmail.com\\
%%yangkang.chen@zju.edu.cn \\
%\footnotemark[2]
%ENSN Lab \\
%Seismology Department \\
%National Research Institute of Astronomy and Geophysics (NRIAG)\\
%Helwan 11731, Egypt\\
%engomar91@ gmail.com\\
%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[4]
%College of Geology and Environment\\
%Xi’an University of Science and Technology\\
%Xi’an, Shaanxi Province, China, 710054 \\
%lwxwyh506673@126.com\\
%\footnotemark[5]Bureau of Economic Geology \\
%John A. and Katherine G. Jackson School of Geosciences \\
%The University of Texas at Austin \\
%University Station, Box X \\
%Austin, TX 78713-8924 \\
%sergey.fomel@beg.utexas.edu\\
%

%\AtEndDocument{}

%\newpage
%\listoffigures

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.8\textwidth]{Fig/fig}}
%	\caption{Caption.}
%	\label{fig:fig}
%\end{figure}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure}

%\begin{figure*}[ht!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig1}
%    \label{fig:fig1}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/fig2}
%    \label{fig:fig2}}\\
%	\caption{(a) Caption a. (b) Caption b.}
%	\label{fig:fig1,fig2}
%\end{figure*}

%\begin{table}[h]
%\caption{Table caption}
%\begin{center}
%     \begin{tabular}{|c|c|c|c|c|c|} 
%	  \hline Column1 (unit)  & Column2 (unit) & Column3 (unit) \\ 
%	  \hline 1 & 2  & 3 \\
%       \hline
%    \end{tabular} 
%\end{center}
%\label{tbl:table1}
%\end{table}

>>>>

\title{A compact program for 3D passive seismic source-location imaging}

\author{Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[2]\footnotemark[3], Min Bai\footnotemark[4],  Xingye Liu\footnotemark[5], Sergey Fomel\footnotemark[1] }
%\author{Authors}

@@

\address{
\footnotemark[1]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
%yangkang.chen@zju.edu.cn \\
\footnotemark[2]
ENSN Lab \\
Seismology Department \\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt\\
engomar91@ gmail.com\\
\footnotemark[3]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
\footnotemark[4] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[5]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
}

@@

\section{Data and Resources}
All datasets and source codes associated with this research are hosted via the Madagascar platform (www.ahay.org) in the form of reproducible research \cite[]{mada2013}. The compact passive imaging package can be found at \\
$https://github.com/chenyk1990/passive\_imaging$.

@@

\inputdir{mod3d}
\plot{data}{width=0.6\textwidth}{Recorded passive seismic data in the synthetic example.}
\multiplot{9}{vel1,location-tr1,location1,vel2,location-tr2,location2,vel3,location-tr3,location3}{width=0.3\textwidth}{\wen{Velocity model and the highlighted first source location (a), its time-reversal imaging result using the traditional (b) and proposed (c) methods. Velocity model and the highlighted second source location (d), its time-reversal imaging result using the traditional (e) and proposed (f) methods. Velocity model and the highlighted third source location (g), its time-reversal imaging result using the traditional (h) and proposed (i) methods.}}
\multiplot{4}{data_mask0,data_mask1,data_mask2,data_mask3}{width=0.45\textwidth}{Four grouped recorded passive seismic data. }

%\inputdir{field3d_geo}
%%\plot{test1}{width=\textwidth}{Separated x-component of the S1 elastic wavefield in the orthorhombic media.}
%\multiplot{4}{rsf_real,sov,f-location-tr,f-location1}{width=0.45\textwidth}{Field data example. (a) Recorded microseismic data. (b) Constructed velocity model. \dlo{(c) 3D source location image.}\wen{(c) 3D source location image using the traditional method. (d) 3D source location image using the proposed method.}}
%
%\inputdir{mod3d_geo_ng}
%\multiplot{4}{data_mask0_ng2,data_mask0_ng6,data_mask0_ng8,data_mask0_ng10}{width=0.45\textwidth}{The first group of recorded data when $N_g=2,6,8,10$, respectively. }
%
%\multiplot{4}{location1-ng2,location1-ng6,location1-ng8,location1-ng10}{width=0.45\textwidth}{The images of the first source location when $N_g=2,6,8,10$, respectively. }
%
%\inputdir{mod3d_geo_noise}
%\multiplot{4}{data-2,data-4,data-6,data-8}{width=0.45\textwidth}{Recorded data when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. The corresponding S/Ns of (a)-(d) are -4.97 dB, -21.96 dB, -34.97 dB, and -41.96 dB, respectively. }
%
%\multiplot{4}{location1-noise2,location1-noise4,location1-noise6,location1-noise8}{width=0.45\textwidth}{The images of the first source location when noise variation $\sigma^2=0.01,0.5,10,50$, respectively. }
%
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr1.rsf 
%%   0:        -1.957
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr2.rsf 
%%   0:        -4.967
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr3.rsf 
%%   0:        -14.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr4.rsf 
%%   0:        -21.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr5.rsf 
%%   0:        -31.96
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr6.rsf 
%%   0:        -34.97
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr7.rsf 
%%   0:        -37.98
%%Yangkangs-MacBook-Pro:mod3d_geo_noise chenyk$ sfdisfil <snr8.rsf 
%%   0:        -41.96
%%  
%
%\inputdir{mod3d_geo_density}
%\multiplot{4}{data-d6,data-d8,data-d9,data-d10}{width=0.45\textwidth}{The observed data with 121, 81, 16, and 8 recorded traces, respectively.  }
%
%\multiplot{4}{location1-density6,location1-density8,location1-density9,location1-density10}{width=0.45\textwidth}{The images of the first source location when there are 121, 81, 16, and 8 recorded traces, respectively. }
% 
\bibliographystyle{seg}
\bibliography{micro}
